Journal and article coverage

### 2025-02-12 analysis/manuscript.Rmd
Tmp save methods

The aim of this study is to demonstrate the suitability of open scholarly data sources for assessing the impact of transformative agreements on hybrid open access.
To achieve this, results from hoaddata, an openly available collection of open research information regarding hybrid open access, was compared with the established bibliometric databases Web of Science and Scopus.
After describing the initial data sources used, the necessary pre-processing steps to obtain eligible articles from transformative agreements using open access evidence, author roles (first and corresponding) and affiliation data are presented.
Overall, xxxx hybrid journals from xxx agreements that published at least one open access article between 2019 and 2023. formed the basis of this study.

@@

hoaddata, developed and maintained by the author, is an R data package comprising information about the uptake of hybrid open access since 2017 from several openly available data sources.
It combines article-level metadata from Crossref and OpenAlex with transformative agreement information from the cOAlition S Journal Checker Tool (JCT), which links journal and institutional data to agreements in the ESAC registry.

More specifically, hoaddata uses Crossref, a DOI registration agency, for obtaining journal publication volume and open access status through
Creative Commons licence information relative to the published version ("version of record").
Because of limited affiliation metadata in Crossref (https://doi.org/10.31222/osf.io/smxe5), hoaddata sources  first-author affiliations from OpenAlex.
While the country in which a first-author was located was used to aggregate country-level statistics, Research Organization Registry (ROR) identifiers (ROR-ID) were used in conjunction with ESAC registry information on the duration of an agreement was used to estimate whether an article was published under active transformative agreements.
This matching benefited from the availability of the ROR-IDs in both sources.
To improve the matching, JCT data were enriched to include associated institutions, such as unviersity hospitals.

hoaddata follows good practices for computational reproducibility using R.
The package, which includes data, code, a test suite and documentation, is openly available on GitHub.
To ensure computational reproducibility while aggregating the data, a GitHub Actions continuous integration and delivery (CI/CD) workflow interfaces with the SUB Göttingen's open scholarly data warehouse based on Google BigQuery, which provides high-performant programmatic access to monthly snapshots of Crossref and OpenAlex.
The package has been regularly updated since 2022 and the version including the computation log is available on GitHub.

hoaddata is used as a data basis of the Hybrid Open Access Dashboard, a data analytics services for  library consortia and publishers to track the uptake of hybrid open access through transformative agreements.
It was also used in bibliometric research (Jahn 2025).

@@

Clarivate Analytics' Web of Science (WoS) is a well-established proprietary bibliometric database consisting of several collections [@Birkle_2020]. 
The collections considered in this study were the Science Citation Index Expanded (SCIE), the Social Sciences Citation Index (SSCI) and the Arts & Humanities Citation Index (AHCI).

The WoS provides important data points for studying spending on open access: author affiliations and roles, differentiation of journal articles into document types representing different types of journal contributions, such as original articles or reviews, and open access status information derived from OurResearch's Unpaywall, the same provider as Openalex. However, it lacks information about journals and articles under transformative agreements.

For programmatic access to article-level data, the database of the Kompetenznetzwerk Bibliometrie (KB) in Germany is used to access bibliometric data. The KB processes raw XML data provided by Clarivate Analytics, which is provided as an in-house PostgreSQL database under a uniform schema.
To support reproducibility, KB maintains annual snapshots of the database. 
Accordingly, this study used the annual snapshot from April 2024, which is considered to cover almost the entire previous publication year [@schmidt_2024_13935407].

@@

Elsevier's Scopus, launched in 2004, is another widely used proprietary bibliometric database for measuring research [@Baas_2020].
Similar to the Web of Science, Scopus is selective with regard to the journals it indexes.
However, its coverage is substantially more extensive than that of the Web of Science Core collection [@Singh_2021; @Visser_2021].
With detailed metadata about article types, open access status information derived from Unpaywall, author roles, and disambiguated affiliations, Scopus also contains important data to assess open access uptake, although no direct information regarding transformative agreements was available at the time of the study.

This study used the Scopus annual snapshot of April 2024 as provided by the KB. The same KB curation effort was applied to the  Scopus raw data as for the Web of Science [@schmidt_2024_13935407].

@@

### journal matching

### authorship records

###  Identifying eligible articles under transformative agreements

@@

>>>>

The aim of this study is to demonstrate the suitability of open scholarly data sources for assessing the impact of transformative agreements on hybrid open access.
To achieve this, results from hoaddata, an openly available collection of open research information regarding hybrid open access, was compared with the established bibliometric databases Web of Science and Scopus.
After describing the initial data sources used, the necessary pre-processing steps to obtain eligible articles from transformative agreements using open access evidence, author roles (first and corresponding) and affiliation data are presented.
<!-- Overall, xxxx hybrid journals from xxx agreements that published at least one open access article between 2019 and 2023. formed the basis of this study. -->

@@

hoaddata, developed and maintained by the author to support open access monitoring and research [@Jahn_2025], is an R data package comprising information about the uptake of hybrid open access since 2017 from several openly available data sources.
It combines article-level metadata from Crossref and OpenAlex with transformative agreement information from the cOAlition S Journal Checker Tool (JCT), which links journal and institutional data to agreements in the ESAC registry.

More specifically, hoaddata uses Crossref, a DOI registration agency, for obtaining journal publication volume and open access status through
Creative Commons licence information relative to the published version ("version of record").
Because of limited affiliation metadata in Crossref [@van_Eck_2022], hoaddata sources first-author affiliations from OpenAlex.

<!--While the country in which a first-author was located was used to aggregate country-level statistics, Research Organization Registry (ROR) identifiers (ROR-ID) were used in conjunction with ESAC registry information on the duration of an agreement was used to estimate whether an article was published under active transformative agreements.
This matching benefited from the availability of the ROR-IDs in both sources.
To improve the matching, JCT data were enriched to include associated institutions, such as unviersity hospitals.-->

hoaddata follows good practices for computational reproducibility using R.
The package, which includes data, code, a test suite and documentation, is openly available on GitHub.
To ensure computational reproducibility while aggregating the data, a GitHub Actions continuous integration and delivery (CI/CD) workflow interfaces with the SUB Göttingen's open scholarly data warehouse based on Google BigQuery, which provides high-performant programmatic access to monthly snapshots of Crossref and OpenAlex.
The workflow has run regularly to fetch updates from these data sources since 2022.
The package version used in this study is 0.3, containing data from the Crossref 2024-08 dump provided to Crossref Metadata Plus subscribers and the OpenAlex 2024-08-29 monthly dump.
This version including the computation log is available on GitHub (https://github.com/subugoe/hoaddata/releases/tag/v.0.3).

@@

Clarivate Analytics' Web of Science (WoS) is a well-established proprietary bibliometric database consisting of several collections [@Birkle_2020]. 
The collections considered in this study were the Science Citation Index Expanded (SCIE), the Social Sciences Citation Index (SSCI) and the Arts & Humanities Citation Index (AHCI), collectively referred to as Web of Science Primary (WoS Primary).

The WoS Primary provides important data points for analysing open access: author affiliations and roles, differentiation of journal articles into document types representing different types of journal contributions, such as original articles or reviews, and open access status information derived from OurResearch's Unpaywall, the same provider as Openalex.
However, it lacks information about journals and articles under transformative agreements.

For programmatic access to article-level data, this study used the database of the Kompetenznetzwerk Bibliometrie (KB) in Germany. The KB processes raw XML data provided by Clarivate Analytics, which is provided as an in-house PostgreSQL database under a uniform schema.
To support reproducibility, KB maintains annual snapshots of the database. 
Accordingly, this study used the annual snapshot from April 2024, wos_b_202404, which is considered to cover almost the entire previous publication year [@schmidt_2024_13935407].

@@

Elsevier's Scopus, launched in 2004, is another widely used proprietary bibliometric database for measuring research [@Baas_2020].
Similar to the Web of Science, Scopus is selective with regard to the journals it indexes.
However, its coverage is substantially more extensive than that of the Web of Science collections considered in this study [@Singh_2021; @Visser_2021].
With detailed metadata about article types, open access status information derived from Unpaywall, author roles, and disambiguated affiliations, Scopus also contains important data to assess open access uptake, although no direct information regarding transformative agreements was available at the time of the study.

This study used the Scopus annual snapshot of April 2024 as provided by the KB (scp_b_202404). The same KB curation effort was applied to the  Scopus raw data as for the Web of Science [@schmidt_2024_13935407].

@@

### Determining hybrid journal publication volume

This study examined the adoption of open access for hybrid journals included in transformative agreements, which published at least one journal article in the five-year period 2019-2023. 
The initial data source was the Transformative Agreements Public Data from the cOAlition S Journal Checker Tool (JCT), which helps authors identify suitable open access publishing venues. 
Weekly snapshots of this data were archived using an automated GitHub Actions workflow (https://github.com/njahn82/jct_data) and into hoaddata.
The resulting JCT data cover agreements active from July 2021 to July 2024.

The JCT journal data was enriched with the linking ISSN (ISSN-L) according to the ISSN Registry Agency.
A comprehensive exclusion of fully open access journals was performed, following the methodology described in @jahn_2025.
This involved checking multiple journal lists (DOAJ, OpenAlex, Bielefeld) and article-level investigations.
The JCT institution data was enriched with ROR-IDs from associated institutions, such as university hospitals or institutes of large research organisations such as the Max Planck Society, according to OpenAlex' institution entity.
<!-- In total, xxxx hybrid journals could be linked to xxx agreements listed in the ESAC Transformative Agreements Registry, which formed to basis for obtaining article-level data including author affiliations, open access status ans document types. -->

For each database, article metadata was retrieved using all ISSN variants linked to an ISSN-L.
The metadata included DOIs, document types (where available), author roles, institutional affiliations, publication dates and open access information.
Publication years were determined using the earliest known date of publication in a journal.
In the case of Crossref, the article data source for hoaddata, this was the issued date, although variations were observed (check ref).
For Web of Science and Scopus, the earliest publication date was used where available.
In the latter case, the KB determined the earliest known publication date by tracking versions of the raw data.

<!-- literature to check https://direct.mit.edu/qss/article/3/1/99/109079/The-prevalence-and-impact-of-university-->

### Open Access

Only published versions with Creative Commons licenses available on publisher platforms were considered as hybrid open access. 
hoaddata derived this information from Crossref's license metadata, while Web of Science and Scopus  used data from Unpaywall. 
In additiaon to Crossref, Unpaywall also parses publisher websites directly, because some publishers do not provide machine-readable Creative Commons license information [@Piwowar_2018], although transformative agreement workflows requiring this information during DOI registration [@Geschuhn_2017].

### Author affiliations

```{r cache=TRUE}
# Article level data TA
ta_oa_inst <- readr::read_csv(here::here("data-raw", "ta_oa_inst.csv"))
```
Author affiliations at the article level were retrieved for both first and, if available, corresponding authors across all databases. 
To handle different address variants, database-specific affiliation identifiers were used: ROR-IDs from OpenAlex for hoaddata, affiliation enhanced names for Web of Science, and Scopus Affiliation Identifiers for Scopus.
Additionally, ISO country codes were retrieved for each author's address to compile country-level statistics. 
These country codes for Web of Science and Scopus were provided by the KB.

Because neither Web of Science nor Scopus support ROR IDs—the institution identifier used by the JCT—a two-step matching process was implemented to identify articles covered by transformative agreements. 
First, `r length(unique(ta_oa_inst$doi))` articles from `r length(unique(ta_oa_inst$ror))` institutions with ROR-IDs in the JCT data since 2017 (according to hoaddata) were processed to map first authors' ROR-IDs to corresponding proprietary affiliation identifier in Web of Science and Scopus using DOI matching.
Then, an algorithm selected the most frequent ROR ID and proprietary identifier pairs to handle multiple affiliations and organizational hierarchy differences.

```{r aff_evaluation}
scp_ror <- readr::read_csv(here::here("data-raw", "scp_wos_matching.csv")) 
wos_ror <- readr::read_csv(here::here("data-raw", "ror_wos_matching.csv")) 
```

This process linked `r length(unique(scp_ror$ror))` ROR IDs to  `r length(unique(scp_ror$vendor_org_id))` Scopus Affiliation IDs, and  `r length(unique(wos_ror$ror))` ROR IDs to `r length(unique(scp_ror$vendor_org_id))` enhanced affiliation strings in the Web of Science. 
Quality evaluation through random sampling of 50 pairs revealed an error rate of 22% for Web of Science (11 mismatches) and 6% for Scopus (3 mismatches). 
Upon inspection, these mismatches primarily occurred with less-represented institutions having only a few publications, introduced through multiple affiliations of single authors. 
The difference between databases suggests that Scopus's affiliation control aligns more closely with ROR than that of the Web of Science.

On the basis of these matching tables, articles eligible under transformative agreements could also be retrieved from the Web of Science and Scopus, although they did not contain the ROR IDs used by the JCT.

### Estimating open access in hybrid journals covered by transformative agreements

@@

As a result of the above-described comprehensive data processing, data-sets were prepared for each database on open access in hybrid journals included in transformative agreements at the country and journal level by year. 
Table \ref{tab:methods_overview_table} presents an general overview of the coverage of hybrid journals in transformative agreements 2019-23 per dataset. 
It shows that the majority of hybrid journals published at least one original article or review (core) in the five-years period.
These journals constituted the basis for the subsequent aggregation of publication metrics. 
While hoad only covers articles with DOI, the aggreation of Scopus and Web of Scienc ewas carried out isng the databse identifier. 
A subsequent compatision of DOU coverage illustrates that non.core articles in Web of Scienc e lack DOIs. These are in aprticular meeting abstracts, a pecularity of this database.
Open access was aggregated using DOI, as all alos Unpaywall only colelctzs opena cces ststaus information for articles with DOI. 
A closer view on core articles with affiliation data reveal a lack of data withr egard to corresponding auhtors in the case of OpenAlex. Only aroud two third of investiaged artilces had at affilation data linked to corresponding authoirs. In case of first authors, the share was higher.
In contrast, web of scienc eand scopus recorded a higher coverage.
Accordingly, only first authro evidence were presented for haoddata in the follwoing

### 2025-02-12 analysis/manuscript.tex
Tmp save methods

The aim of this study is to demonstrate the suitability of open
scholarly data sources for assessing the impact of transformative
agreements on hybrid open access. To achieve this, results from
hoaddata, an openly available collection of open research information
regarding hybrid open access, was compared with the established
bibliometric databases Web of Science and Scopus. After describing the
initial data sources used, the necessary pre-processing steps to obtain
eligible articles from transformative agreements using open access
evidence, author roles (first and corresponding) and affiliation data
are presented. Overall, xxxx hybrid journals from xxx agreements that
published at least one open access article between 2019 and 2023. formed
the basis of this study.

@@

hoaddata, developed and maintained by the author, is an R data package
comprising information about the uptake of hybrid open access since 2017
from several openly available data sources. It combines article-level
metadata from Crossref and OpenAlex with transformative agreement
information from the cOAlition S Journal Checker Tool (JCT), which links
journal and institutional data to agreements in the ESAC registry.

More specifically, hoaddata uses Crossref, a DOI registration agency,
for obtaining journal publication volume and open access status through
Creative Commons licence information relative to the published version
(``version of record''). Because of limited affiliation metadata in
Crossref (\url{https://doi.org/10.31222/osf.io/smxe5}), hoaddata sources
first-author affiliations from OpenAlex. While the country in which a
first-author was located was used to aggregate country-level statistics,
Research Organization Registry (ROR) identifiers (ROR-ID) were used in
conjunction with ESAC registry information on the duration of an
agreement was used to estimate whether an article was published under
active transformative agreements. This matching benefited from the
availability of the ROR-IDs in both sources. To improve the matching,
JCT data were enriched to include associated institutions, such as
unviersity hospitals.

hoaddata follows good practices for computational reproducibility using
R. The package, which includes data, code, a test suite and
documentation, is openly available on GitHub. To ensure computational
reproducibility while aggregating the data, a GitHub Actions continuous
integration and delivery (CI/CD) workflow interfaces with the SUB
Göttingen's open scholarly data warehouse based on Google BigQuery,
which provides high-performant programmatic access to monthly snapshots
of Crossref and OpenAlex. The package has been regularly updated since
2022 and the version including the computation log is available on
GitHub.

hoaddata is used as a data basis of the Hybrid Open Access Dashboard, a
data analytics services for library consortia and publishers to track
the uptake of hybrid open access through transformative agreements. It
was also used in bibliometric research (Jahn 2025).

@@

Clarivate Analytics' Web of Science (WoS) is a well-established
proprietary bibliometric database consisting of several collections
(Birkle et al., 2020). The collections considered in this study were the
Science Citation Index Expanded (SCIE), the Social Sciences Citation
Index (SSCI) and the Arts \& Humanities Citation Index (AHCI).

The WoS provides important data points for studying spending on open
access: author affiliations and roles, differentiation of journal
articles into document types representing different types of journal
contributions, such as original articles or reviews, and open access
status information derived from OurResearch's Unpaywall, the same
provider as Openalex. However, it lacks information about journals and
articles under transformative agreements.

For programmatic access to article-level data, the database of the
Kompetenznetzwerk Bibliometrie (KB) in Germany is used to access
bibliometric data. The KB processes raw XML data provided by Clarivate
Analytics, which is provided as an in-house PostgreSQL database under a
uniform schema. To support reproducibility, KB maintains annual
snapshots of the database. Accordingly, this study used the annual
snapshot from April 2024, which is considered to cover almost the entire
previous publication year (Schmidt et al., 2024).

@@

Elsevier's Scopus, launched in 2004, is another widely used proprietary
bibliometric database for measuring research (Baas et al., 2020).
Similar to the Web of Science, Scopus is selective with regard to the
journals it indexes. However, its coverage is substantially more
extensive than that of the Web of Science Core collection (Singh et al.,
2021; Visser et al., 2021). With detailed metadata about article types,
open access status information derived from Unpaywall, author roles, and
disambiguated affiliations, Scopus also contains important data to
assess open access uptake, although no direct information regarding
transformative agreements was available at the time of the study.

This study used the Scopus annual snapshot of April 2024 as provided by
the KB. The same KB curation effort was applied to the Scopus raw data
as for the Web of Science (Schmidt et al., 2024).

@@

\subsubsection{journal matching}\label{journal-matching}

\subsubsection{authorship records}\label{authorship-records}

\subsubsection{Identifying eligible articles under transformative
agreements}\label{identifying-eligible-articles-under-transformative-agreements}

@@

>>>>

The aim of this study is to demonstrate the suitability of open
scholarly data sources for assessing the impact of transformative
agreements on hybrid open access. To achieve this, results from
hoaddata, an openly available collection of open research information
regarding hybrid open access, was compared with the established
bibliometric databases Web of Science and Scopus. After describing the
initial data sources used, the necessary pre-processing steps to obtain
eligible articles from transformative agreements using open access
evidence, author roles (first and corresponding) and affiliation data
are presented.

@@

hoaddata, developed and maintained by the author to support open access
monitoring and research (Jahn, 2025), is an R data package comprising
information about the uptake of hybrid open access since 2017 from
several openly available data sources. It combines article-level
metadata from Crossref and OpenAlex with transformative agreement
information from the cOAlition S Journal Checker Tool (JCT), which links
journal and institutional data to agreements in the ESAC registry.

More specifically, hoaddata uses Crossref, a DOI registration agency,
for obtaining journal publication volume and open access status through
Creative Commons licence information relative to the published version
(``version of record''). Because of limited affiliation metadata in
Crossref (Eck \& Waltman, 2022), hoaddata sources first-author
affiliations from OpenAlex.

hoaddata follows good practices for computational reproducibility using
R. The package, which includes data, code, a test suite and
documentation, is openly available on GitHub. To ensure computational
reproducibility while aggregating the data, a GitHub Actions continuous
integration and delivery (CI/CD) workflow interfaces with the SUB
Göttingen's open scholarly data warehouse based on Google BigQuery,
which provides high-performant programmatic access to monthly snapshots
of Crossref and OpenAlex. The workflow has run regularly to fetch
updates from these data sources since 2022. The package version used in
this study is 0.3, containing data from the Crossref 2024-08 dump
provided to Crossref Metadata Plus subscribers and the OpenAlex
2024-08-29 monthly dump. This version including the computation log is
available on GitHub
(\url{https://github.com/subugoe/hoaddata/releases/tag/v.0.3}).

@@

Clarivate Analytics' Web of Science (WoS) is a well-established
proprietary bibliometric database consisting of several collections
(Birkle et al., 2020). The collections considered in this study were the
Science Citation Index Expanded (SCIE), the Social Sciences Citation
Index (SSCI) and the Arts \& Humanities Citation Index (AHCI),
collectively referred to as Web of Science Primary (WoS Primary).

The WoS Primary provides important data points for analysing open
access: author affiliations and roles, differentiation of journal
articles into document types representing different types of journal
contributions, such as original articles or reviews, and open access
status information derived from OurResearch's Unpaywall, the same
provider as Openalex. However, it lacks information about journals and
articles under transformative agreements.

For programmatic access to article-level data, this study used the
database of the Kompetenznetzwerk Bibliometrie (KB) in Germany. The KB
processes raw XML data provided by Clarivate Analytics, which is
provided as an in-house PostgreSQL database under a uniform schema. To
support reproducibility, KB maintains annual snapshots of the database.
Accordingly, this study used the annual snapshot from April 2024,
wos\_b\_202404, which is considered to cover almost the entire previous
publication year (Schmidt et al., 2024).

@@

Elsevier's Scopus, launched in 2004, is another widely used proprietary
bibliometric database for measuring research (Baas et al., 2020).
Similar to the Web of Science, Scopus is selective with regard to the
journals it indexes. However, its coverage is substantially more
extensive than that of the Web of Science collections considered in this
study (Singh et al., 2021; Visser et al., 2021). With detailed metadata
about article types, open access status information derived from
Unpaywall, author roles, and disambiguated affiliations, Scopus also
contains important data to assess open access uptake, although no direct
information regarding transformative agreements was available at the
time of the study.

This study used the Scopus annual snapshot of April 2024 as provided by
the KB (scp\_b\_202404). The same KB curation effort was applied to the
Scopus raw data as for the Web of Science (Schmidt et al., 2024).

@@

\subsubsection{Determining hybrid journal publication
volume}\label{determining-hybrid-journal-publication-volume}

This study examined the adoption of open access for hybrid journals
included in transformative agreements, which published at least one
journal article in the five-year period 2019-2023. The initial data
source was the Transformative Agreements Public Data from the cOAlition
S Journal Checker Tool (JCT), which helps authors identify suitable open
access publishing venues. Weekly snapshots of this data were archived
using an automated GitHub Actions workflow
(\url{https://github.com/njahn82/jct_data}) and into hoaddata. The
resulting JCT data cover agreements active from July 2021 to July 2024.

The JCT journal data was enriched with the linking ISSN (ISSN-L)
according to the ISSN Registry Agency. A comprehensive exclusion of
fully open access journals was performed, following the methodology
described in (\textbf{jahn\_2025?}). This involved checking multiple
journal lists (DOAJ, OpenAlex, Bielefeld) and article-level
investigations. The JCT institution data was enriched with ROR-IDs from
associated institutions, such as university hospitals or institutes of
large research organisations such as the Max Planck Society, according
to OpenAlex' institution entity.

For each database, article metadata was retrieved using all ISSN
variants linked to an ISSN-L. The metadata included DOIs, document types
(where available), author roles, institutional affiliations, publication
dates and open access information. Publication years were determined
using the earliest known date of publication in a journal. In the case
of Crossref, the article data source for hoaddata, this was the issued
date, although variations were observed (check ref). For Web of Science
and Scopus, the earliest publication date was used where available. In
the latter case, the KB determined the earliest known publication date
by tracking versions of the raw data.

\subsubsection{Open Access}\label{open-access}

Only published versions with Creative Commons licenses available on
publisher platforms were considered as hybrid open access. hoaddata
derived this information from Crossref's license metadata, while Web of
Science and Scopus used data from Unpaywall. In additiaon to Crossref,
Unpaywall also parses publisher websites directly, because some
publishers do not provide machine-readable Creative Commons license
information (Piwowar et al., 2018), although transformative agreement
workflows requiring this information during DOI registration (Geschuhn
\& Stone, 2017).

\subsubsection{Author affiliations}\label{author-affiliations}

Author affiliations at the article level were retrieved for both first
and, if available, corresponding authors across all databases. To handle
different address variants, database-specific affiliation identifiers
were used: ROR-IDs from OpenAlex for hoaddata, affiliation enhanced
names for Web of Science, and Scopus Affiliation Identifiers for Scopus.
Additionally, ISO country codes were retrieved for each author's address
to compile country-level statistics. These country codes for Web of
Science and Scopus were provided by the KB.

Because neither Web of Science nor Scopus support ROR IDs---the
institution identifier used by the JCT---a two-step matching process was
implemented to identify articles covered by transformative agreements.
First, 2,782,540 articles from 6,457 institutions with ROR-IDs in the
JCT data since 2017 (according to hoaddata) were processed to map first
authors' ROR-IDs to corresponding proprietary affiliation identifier in
Web of Science and Scopus using DOI matching. Then, an algorithm
selected the most frequent ROR ID and proprietary identifier pairs to
handle multiple affiliations and organizational hierarchy differences.

This process linked 6,375 ROR IDs to 4,894 Scopus Affiliation IDs, and
6,034 ROR IDs to 4,894 enhanced affiliation strings in the Web of
Science. Quality evaluation through random sampling of 50 pairs revealed
an error rate of 22\% for Web of Science (11 mismatches) and 6\% for
Scopus (3 mismatches). Upon inspection, these mismatches primarily
occurred with less-represented institutions having only a few
publications, introduced through multiple affiliations of single
authors. The difference between databases suggests that Scopus's
affiliation control aligns more closely with ROR than that of the Web of
Science.

On the basis of these matching tables, articles eligible under
transformative agreements could also be retrieved from the Web of
Science and Scopus, although they did not contain the ROR IDs used by
the JCT.

\subsubsection{Estimating open access in hybrid journals covered by
transformative
agreements}\label{estimating-open-access-in-hybrid-journals-covered-by-transformative-agreements}

@@

\bibitem[\citeproctext]{ref-van_Eck_2022}
Eck, N. J. van, \& Waltman, L. (2022). \emph{Crossref as a source of
open bibliographic metadata}.
\url{https://doi.org/10.31222/osf.io/smxe5}

\bibitem[\citeproctext]{ref-Geschuhn_2017}
Geschuhn, K., \& Stone, G. (2017). It's the workflows, stupid! What is
required to make {``offsetting''} work for the open access transition.
\emph{Insights the {UKSG} Journal}, \emph{30}(3), 103--114.
\url{https://doi.org/10.1629/uksg.391}

\bibitem[\citeproctext]{ref-Jahn_2025}
Jahn, N. (2025). How open are hybrid journals included in transformative
agreements? \emph{Quantitative Science Studies}, 1--39.
\url{https://doi.org/10.1162/qss_a_00348}

\bibitem[\citeproctext]{ref-Piwowar_2018}
Piwowar, H., Priem, J., Larivière, V., Alperin, J. P., Matthias, L.,
Norlander, B., Farley, A., West, J., \& Haustein, S. (2018). The state
of {OA}: A large-scale analysis of the prevalence and impact of open
access articles. \emph{{PeerJ}}, \emph{6}, e4375.
\url{https://doi.org/10.7717/peerj.4375}
